\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-01-14 AffineLieAlgebras/InformalNotes/article.tex
Fixed missed case of $B_r$ subalgebras

For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$. So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$. Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}.

>>>>

For the algebra $\mathfrak{g}$ from the series $B_r$ the roots in the orthogonal basis $\{e_i,\; 1\leq i\leq r\}$ are $\Delta=\{\alpha_{\pm i,\pm j}=\pm e_i\pm e_j,\;i<j;\; \alpha_{\pm j}=\pm e_{ j},\; 1\leq j\leq r\}$, $\Delta^{+}=\{\alpha_{i,-j},\; \alpha_{ij},\; \alpha_j;\; i<j,\; 1\leq j\leq r\}$ and the set of simple roots consists of $\alpha_{1,-2},\alpha_{2,-3},\dots,\alpha_{r-1,-r},\alpha_r$. So if the regular subalgebra $\mathfrak{a}=A_{r_{\mathfrak{a}}}$ and its simple root system consists of first $r_{\mathfrak{a}}$ simple roots, then $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}+1<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}-1}$. Otherwise if $\mathfrak{a}=B_{r_{\mathfrak{a}}}$ and its simple roots are $\alpha_{r-r_{\mathfrak{a}}+1,-r+r_{\mathfrak{a}}-2},\dots,\alpha_{r-1,r},\alpha_r$ we see that $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; 1<i<j\leq r-r_{\mathfrak{a}}\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$. It is the only case when simple roots of $\mathfrak{a}_{\bot}$ can not be obtained from the extended Dynkin diagram, as can be seen in the Table \ref{tab:diagrams}. 
There exists the third possibility to get the pair of subalgebras $\mathfrak{a},\mathfrak{a}_{\bot}$ with the regular subalgebra $\mathfrak{a}$ by dropping single node from the extended Dynkin diagram of $B_r$. It can be done by taking as the set of simple roots of $\mathfrak{a}$ the set $\{\alpha_{1,-2},\alpha_{1,2},\alpha_{2,-3},\dots,\alpha_{r_{\mathfrak{a}}-1,-r_{\mathfrak{a}}}\}$. Then $\mathfrak{a}=D_{r_{\mathfrak{a}}}$, $\Delta_{\mathfrak{a}_{\bot}}=\{\alpha_{\pm i,\pm j},\;\alpha_j,\; r_{\mathfrak{a}}<i<j\leq r\}$ and $\mathfrak{a}_{\bot}=B_{r-r_{\mathfrak{a}}}$.
